Cosmic Web

### 2014-02-04 paper/main.tex
more text

\begin{equation}
T_{ij} = \frac{\partial^2 \psi}{\partial r_i \partial r_j}, 
\end{equation}
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates.

@@

\begin{equation}
FA=
\end{equation}
%
an additional advantage of the FA is that it does not depend on the
choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
kinds of tidal forces on the Local Group.

@@

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}

@@

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
\end{center}
\caption{Density and Fractional Anisotropy distribution for the pairs in the general and $3\sigma$ samples.
    \label{fig:FA}}  
\end{figure}

>>>>

\begin{equation}
T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
\end{equation}
where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
coordiates and $\phi$ is the gravitational potential renormalized to
follow the following Poisson equation $\nabla\phi=\delta$ where
$\delta$ is the matter overdensity.

@@

\begin{equation}
{\mathrm FA}=\frac{1}{\sqrt{3}}\sqrt{\frac{(\lambda_1- \lambda_3)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{\lambda_1^2+\lambda_2^2 + \lambda_3^2}}.
\end{equation}
%
An additional advantage of the FA is that it does not depend on the
choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
kinds of tidal forces on the Local Group.

@@

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
3$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the same number as a percentage of the
total population. 
\label{table:web_type}}
\end{center}
\end{table}

The next result is related to the matter overdensity for the LG
samples. Figure \ref{fig:density} shows that the range of
overdensities for the general pair sample spans almost two orders of
magnitude from underdense regions $\delta<0$ to high density regions
$\delta\sim 30$, with a distribution peaking around $\delta \sim
0$. In contrast the $2\sigma$ and $3\sigma$ samples are located within
a narrower range of overdensities $0.0<\delta<4.0$ peaking at $\delta
\sim 1.5$. These values are consistent with the fact that these
samples are mostly found in filaments and sheets.

In Figure \ref{fig:FA} we show the integrated distribution for the
Fractional Anisotropy in the tree samples. The General Sample clusters
towards values of ${\mathrm FA}\sim 1.0$, while the $2\sigma$ and
$3\sigma$ prefer values around $0.6$.

In Figure \ref{fig:delta_FA} we present a joint scatter plot for the
overdensity and fractional anisotropy. For clarity we only include the
general and $3\sigma$ samples. In this plane we observe from the general
sample that there are broad correlations between the overdensity and
the fractional anisotropy.

\begin{figure}
\begin{center}
  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
\end{center}
\caption{Density and Fractional Anisotropy distribution for the pairs
  in the general and $3\sigma$ samples. 
    \label{fig:delta_FA}}  
\end{figure}

@@
